Approximation as Differentiation

### 2025-05-21 main/framework.tex
Improvements to 3.1.

This pattern of objects and morphisms is exactly the \emph{Grothendieck construction} for a particular indexed
category $T: \Set^\op \to \Cat$, namely the functor which assigns to every set $X$ the functor category $T(X)
= \Func{X}{\LatGal}$. Here the (discrete) category $X$ is a plain set and so $\Func{X}{\LatGal}$ is exactly
the category of $X$-indexed families of bounded lattices, with $X$-indexed families of Galois connections
between them as morphisms. The Grothendieck construction $\Grothendieck{}T$~(\defref{Grothendieck} below) is
the category of all $\Set$-indexed families of bounded lattices, together with morphisms that account for both
structure within each family and how families transform under reindexing.

>>>>

This pattern of objects and morphisms is exactly the \emph{Grothendieck construction} for a particular indexed
category $\Set^\op \to \Cat$, namely the indexed category $\Func{-}{\LatGal}$ which assigns to every set $X$
the functor category $\Func{X}{\LatGal}$. Here the (discrete) category $X$ is a plain set and so
$\Func{X}{\LatGal}$ is exactly the category of $X$-indexed families of bounded lattices, with $X$-indexed
families of Galois connections between them as morphisms. The Grothendieck construction
$\Grothendieck{}T$~(\defref{Grothendieck} below) for an indexed category $T$, sometimes called the \emph{total
category} for $T$, is the category of all $\Set$-indexed families of objects of $T$, together with morphisms
that account for both structure within each family and how families transform under reindexing.
